Learning features and abstract actions for computing generalized plans

### 2018-09-05 doc/paper.tex
Draft sent to H

@@

Generalized planning studies the computation of plans for  solving  multiple  instances at once
\cite{srivastava08learning,bonet09automatic,srivastava:generalized,hu:generalized,BelleL16,anders:generalized}.
For example, the plan  that iteratively  picks  a  clear block above $x$ 
and places it  on the table, achieves the goal $clear(x)$
in \emph{any} instance of the blocks world where the gripper is initially empty.
Once this  general plan or  policy is derived it can be  applied to solve an infinite collection
of instances that involve different initial states, different objects, and hence  different (ground)  actions.

@@

For each transition  $(s, s') \in \S$ and each feature $f \in \F$,
$\Delta_f(s, s') \in \{+, -, \uparrow, \downarrow, \bot\}$ will denote the
\emph{qualitative change of value} of feature $f$ along the transition $(s, s')$,
which can go from false to true ($+$), from true to false ($-$) or remain
unchanged ($\bot$), for boolean features, and can increase ($\uparrow$),
decrease ($\downarrow$), or remain unchanged ($\bot$), for numerical features.
The \emph{propositional variables} in $T(\S,\F)$ are then:
\begin{enumerate}[{\small$\bullet$}]
  \item $selected(f)$ for each $f \in \F$, true iff $f$ selected (in $F$).
  \item $D_1(s,t)$ for states $s$ and $t$ expanded in $\S$,  true iff
    selected features distinguish $s$ from $t$; i.e.\ if $s$ and $t$ disagree
    on the truth value of a selected boolean feature $p$ or atom $n=0$ for a
    selected numerical feature $n$.
    %Since $D_1$ is symmetric, only symbols for $s < t$ are created for some
    %arbitrary, fixed order over the states in $\S_1$.
  \item $D_2(s, s', t, t')$ for each $(s, s')$ and $(t, t')$ in $\S$,
    true iff selected features $f$ distinguish the two transitions; i.e., if
    $\Delta_f(s, s')\not=\Delta_f(t,t')$. 
    %As for $D_1$, the number of $D_2$ variables is cut in half due to symmetries.
\end{enumerate}

@@

The DL grammar is given by the rules: \textcolor{red}{\bf **** More details?}
\begin{enumerate}[{\small$\bullet$}]
  \item $C \ \leftarrow\ \ C_p, C_u, C_x$: primitive, universal, and nominal c's,\footnote{Denotation of $C_x$ for parameter $x$ is $\{x\}$.}
  \item $C \ \leftarrow\  \neg C, C \sqcap C'$: negation and conjunction, 
  \item $C \ \leftarrow\  \exists R.C , \forall R.C$: concepts that use of  roles: first denotes $x$ s.t. for some  $y$,  $R(x,y) \land C(y)$.
  Second,  $x$ s.t. for all $y$, $R(x,y) \rightarrow C(y)$,
  \item $C \ \leftarrow\  R=R'$: stands for $x$ s.t. set of $y$'s  s.t. $R(x,y)$ equal to set of $y$'s s.t. $R'(x,y)$,
    \item $R \leftarrow R_p, R^{-1}, R^*$: primitive, inverse, transitive closure.
%     \item $R \leftarrow R \circ R'$, role composition: $(x,y)$ in $R \circ R'$ if $(x,z)$ in $R$ and $(z,y)$ in $R'$.
%     \item $R \leftarrow R:C$, denotes pairs $(x,y)$ in $R$ s.t. $C(y)$.
 \end{enumerate}

@@

The pool $\F=\F^k$  is defined from $\G^k$ and contains
the  features $f$ that represent the functions $\phi_f(s)$ as follows:
\begin{enumerate}[{\small$\bullet$}]
\item Boolean $b_p$ for each primitive predicate $p$ of arity $0$,
\item Boolean $b_C$ for each $C$ that are true in $s$ iff $|C^s| > 0$,
\item Numerical $n_C$ for each $C$ that stand for cardinality $|C^s|$,
\item Numerical $\textit{dist}(C_1,R:C,C_2)$, that represent that smallest
  $n$ such that for $x_1, \ldots, x_n$, $C_1^s(x_1)$, $C_2^s(x_{n})$, and
  $(R:C)(x_i,x_{i+1})$ for $i=1, \ldots, n$. 
\end{enumerate}

@@

We evaluate the computational model described in steps 1--6 above over several domains.
%

% *Fill up general details in 1--6 that don't change from problem to problem
%how $\S$ obtained
The sample set $\mathcal{S}$ is obtained following one of two possible strategies.
In the \emph{exhaustive} sampling strategy,
$\S$ contains, for every one of the training instances $P$,
all the states generated on a breadth-first search from the initial state in $P$
that is run until $m$ expansions have been performed. If that set includes no goal state,
an optimal plan for $P$ is computed and all of the states along the plan are included in $\S$ as well,
as we need at least one goal state in the sample set.
%
In the \emph{random} sampling strategy, a large number $M$ of states are generated, potentially exhausting the full state space,
and then a certain number $m \ll M$ of them is sampled uniformly at random. If no goal state is found among those $m$,
one random goal state from the larger set is drawn at random and added into the sample.
\textcolor{red}{\bf **** What if $M$ doesn't have a goal? ****}

@@

** Details on the FOND planner, QNP translation, etc. **

@@

The goal marking scheme that  yields the smaller  theory $T_G(\S}, \F)$ is obtained an optimal plan over
a few (always less than xxxx) instances $P$. ??

@@

\newcommand{\rowspacing[1]}{&&&&&&&&&&&&&&&\\[\dimexpr-\normalbaselineskip+2pt]}

\begin{tabular}{%
@{}l%
@{\extracolsep{1.5em}}r%@{}l%
@{\extracolsep{1.5em}}r%
@{\extracolsep{8pt}}r%
%
@{\extracolsep{1.5em}}r%
@{\extracolsep{8pt}}r%
@{\extracolsep{8pt}}r%
@{\extracolsep{8pt}}r%
%
@{\extracolsep{1.5em}}r%
@{\extracolsep{8pt}}r%
@{\extracolsep{8pt}}r%
@{\extracolsep{8pt}}r%
%
@{\extracolsep{1.5em}}r%
@{\extracolsep{8pt}}r%
@{\extracolsep{8pt}}r%
@{\extracolsep{8pt}}r%
%
@{}}

% @{\extracolsep{3pt}}

 & $I$ & $\abs{\S}$ & $k$ & $\abs{\F^k}$ & \multicolumn{2}{c}{$T$} & \multicolumn{2}{c}{$T_G$} &  $C_{\text{SAT}}$ & $\abs{F}$ & $\abs{A_F}$ & $\abs{I_F}$  & $\abs{G_F}$ & $\abs{Q^+_F}$ & $C_{\text{FOND}}$ \\ %

\rowspacing 
\cline{6-7} \cline{8-9}%
\rowspacing

 & &     &      &         & $\#V$ & $\#C$           & $\#V$ & $\#C$             &     &&&&&& \\%

\rowspacing \hline \rowspacing
\multirow{1}{*}{$\Q_{clear}$}
& 1     &     927 & 8  & 322 & 535K & 59.6M & 7.7K & 767K   &  0.01 & 3 & 2   &  - & - & - & - \\% Total complexity of F: 8

\rowspacing \hline \rowspacing
\multirow{1}{*}{$\Q_{on}$}
& 3 &        420  & 8 & 657 & 128K & 25.8M & 18.3K &     3.3M    &  0.02&  5 & 7   &  - & - & - & - \\% Total complexity of F: 18
% Max-sat problem has 128217 variables and 25825428 unique clauses (with repetitions: 25825428). Top weight is 4577

\rowspacing \hline \rowspacing
\multirow{1}{*}{$\Q_{gripper}$}    
& 2 &         403 & 8 & 130 & 93K & 4.7M & 8.1K &   358K    &  0.01 & 4 & 5&  - & - & - & - \\% Total complexity of F: 10

\rowspacing \hline \rowspacing
\multirow{1}{*}{$\Q_{reward}$}
& 2 &         568 & 8 & 280 & 184K & 11.9M & 15.9K & 1.2M   &  0.01 & 2 & 2 &  - & - & - & - \\% Total complexity of F: ?
\end{tabular}

}
\caption{{
  Experimental Results on 4 different generalized planning problems. 
  $I$: number of training instances; 
  $\abs{\S}$: sample set size, in total number of transitions;
  $k$: max. feature comlexity; $\abs{\F^k}$: size of the pool of features;
  $\#V$, $\#C$: Number of variables and clauses of the theories $T(\S,\F)$ and $T_G(\S,\F)$;
  $C_{\text{SAT}}$, $C_{\text{FOND}}$: computation time (sec.) of the SAT and FOND solvers, resp.;
  $\abs{F}$: number of selected features;
  $\abs{A_F}$: number of abstract actions;
  $\abs{I_F}$: ???;
  $\abs{G_F}$: ??? ;
  $\abs{Q^+_F}$: ??? .
  All figures that depend on the SAT theory are given for $T_G(\S,\F)$.
}}
\label{tab:exp-result-data}
\end{table*}
% 2018-09-05 00:54:08 INFO     Selected (states / goals / optimal tx): 220 / 34 / 20

@@

\paragraph{Clearing a block.}
The generalized problem $\Q_{clear}$ aims at achieving the goal $clear(x)$ for any block $x$
in the Blocksworld.
We take the standard STRIPS representation with primitive predicates $on(a, b)$, $clear(b)$, $ontable(b)$, $holding(b)$ and $handempty$.
%
With one single instance $\Q_{clear}$ with 5 blocks, we are able to learn
an abstract action model which features two actions:

- \emph{pick-above-$x$}: \tuple{\neg X, \neg H, n(x) > 0; n(x) \downarrow},

- \emph{place-aside}: \tuple{\neg X, H; \neg H},

\noindent both described in terms of features $H: \abs{holding}$, $X: \abs{holding \sqcap \set{x}}$ and $n(x)\equiv \abs{\exists on^* . \set{x}}$, 
that denote, respectively, whether any block is being held, whether block $x$ is being held,
and the number of blocks above $x$.\footnote{
Action and features names are assigned manually by us to increase readability, but correspond faithfully
to the learnt entities.
}
%
The model is provably correct, but not complete in general, as it lacks e.g.
any action to pick block $x$.
However, it is sufficient to obtain a policy with a single loop that will 
alternatively \emph{pick-above-$x$} and \emph{place-aside} until block $x$ is clear,
which provably \emph{achieves the goal from any configuration of blocks, for any number of blocks}.

% Action 1:
%         PRE: NOT holding(a), bool[holding]
%         EFFS: NOT bool[holding]
% 
% Action 2:
%         PRE: NOT bool[holding], NOT holding(a), n(a) > 0
%         EFFS: DEC n(a), bool[holding]

@@

\paragraph{Stacking two blocks from different towers.}
The problem $\Q_{on}$ is aims at achieving a goal of the form $on(x,y)$
in the Blocksworld for any two blocks $x$ and $y$ that are initially not in the same tower.
We take the same STRIPS representation as above. Based on 3 different instances with up to 14
blocks, we are able to learn an abstract action model with 5 features and 7 actions.
The set of features is made up of  $X$, $n(x)$ and $n(y)$, with the same syntax and semantics as given before,
as well as $E: handempty$
and $XY: [(\exists on^{-1} . \set{x})\sqcap \set{b}]$,
the second of which precisely denotes that block $x$ is on block $y$.

The set of actions includes actions to pick up the topmost block above $x$, to pick up the topmost block above $y$,
to put a block being held \emph{aside}, i.e. not above $x$ nor above $y$, to pick $x$, 
to place $x$ on $y$ and to place $x$ on the table.

- \emph{pick-up-above-$x$}:

- \emph{pick-up-above-$y$}:

@@

DISCUSS POLICY WHEN AVAILABLE. / 
DISCUSS WHY WOULDN'T WORK WHEN IN SAME TOWER.

@@

- $C: \exists carry . \top$ (number of balls carried by the robot),

- $X: at\_robby \sqcap \set{x}$ (whether robot in target room),

- $G: \abs{free}$ (number of empty grippers), and

- $B: \exists at . \neg \set{x}$ (number of balls not in target room),

@@

- \emph{drop-ball(s)-at-$x$}: \tuple{C>0, X;  C\downarrow, G \uparrow}

- \emph{move-to-$x$-half-loaded}: \tuple{\neg X, B=0, C>0, G>0;   X}

- \emph{move-to-$x$-fully-loaded}: \tuple{\neg X, C>0, G=0;   X}

- \emph{pick-ball-not-in-$x$}: \tuple{\neg X, B > 0, G > 0;   B \downarrow, G \downarrow, C\uparrow}

- \emph{drop-$x$}: \tuple{X, C=0, G > 0;   \neg X}

@@

The policy that results ... (!!??)

@@

*** XXX ***

>>>>

\renewcommand\labelitemi{\raisebox{0.4ex}{\tiny$\bullet$}} %% Decrease size of items in enumerate and raise them to center them vertically

@@

Generalized planning studies the computation of plans for  solving  multiple  instances at once
\cite{srivastava08learning,bonet09automatic,srivastava:generalized,hu:generalized,BelleL16,anders:generalized}.
For example, the plan  that iteratively  picks  a  clear block above $x$ 
and places it  on the table, achieves the goal $clear(x)$
in \emph{any} instance of the Blocksworld where the gripper is initially empty.
Once this  general plan or  policy is derived it can be  applied to solve an infinite collection
of instances that involve different initial states, different objects, and hence  different (ground)  actions.

@@

For each transition  $(s, s') \in \S$ and each feature $f \in \F$,
$\Delta_f(s, s') \in \{+, -, \uparrow, \downarrow, \bot\}$ will denote the
\emph{qualitative change of value} of feature $f$ along the transition $(s, s')$,
which can go from false to true ($+$), from true to false ($-$) or remain
unchanged ($\bot$), for boolean features, and can increase ($\uparrow$),
decrease ($\downarrow$), or remain unchanged ($\bot$), for numerical features.
The \emph{propositional variables} in $T(\S,\F)$ are then:
\begin{itemize}
  \item $selected(f)$ for each $f \in \F$, true iff $f$ selected (in $F$).
  \item $D_1(s,t)$ for states $s$ and $t$ expanded in $\S$,  true iff
    selected features distinguish $s$ from $t$; i.e.\ if $s$ and $t$ disagree
    on the truth value of a selected boolean feature $p$ or atom $n=0$ for a
    selected numerical feature $n$.
    %Since $D_1$ is symmetric, only symbols for $s < t$ are created for some
    %arbitrary, fixed order over the states in $\S_1$.
  \item $D_2(s, s', t, t')$ for each $(s, s')$ and $(t, t')$ in $\S$,
    true iff selected features $f$ distinguish the two transitions; i.e., if
    $\Delta_f(s, s')\not=\Delta_f(t,t')$. 
    %As for $D_1$, the number of $D_2$ variables is cut in half due to symmetries.
\end{itemize}

@@

The DL grammar is given by the rules: \textcolor{red}{\bf **** More details?}
\begin{itemize}
  \item $C \ \leftarrow\ \ C_p, C_u, C_x$: primitive, universal, and nominal c's,\footnote{Denotation of $C_x$ for parameter $x$ is $\{x\}$.}
  \item $C \ \leftarrow\  \neg C, C \sqcap C'$: negation and conjunction, 
  \item $C \ \leftarrow\  \exists R.C , \forall R.C$: concepts that use of  roles: first denotes $x$ s.t. for some  $y$,  $R(x,y) \land C(y)$.
  Second,  $x$ s.t. for all $y$, $R(x,y) \rightarrow C(y)$,
  \item $C \ \leftarrow\  R=R'$: stands for $x$ s.t. set of $y$'s  s.t. $R(x,y)$ equal to set of $y$'s s.t. $R'(x,y)$,
    \item $R \leftarrow R_p, R^{-1}, R^*$: primitive, inverse, transitive closure.
%     \item $R \leftarrow R \circ R'$, role composition: $(x,y)$ in $R \circ R'$ if $(x,z)$ in $R$ and $(z,y)$ in $R'$.
%     \item $R \leftarrow R:C$, denotes pairs $(x,y)$ in $R$ s.t. $C(y)$.
 \end{itemize}

@@

The pool $\F=\F^k$  is defined from $\G^k$ and contains
the  features $f$ that represent the functions $\phi_f(s)$ as follows:
\begin{itemize}
\item Boolean $b_p$ for each primitive predicate $p$ of arity $0$,
\item Boolean $b_C$ for each $C$ that are true in $s$ iff $|C^s| > 0$,
\item Numerical $n_C$ for each $C$ that stand for cardinality $|C^s|$,
\item Numerical $\textit{dist}(C_1,R:C,C_2)$, that represent that smallest
  $n$ such that for $x_1, \ldots, x_n$, $C_1^s(x_1)$, $C_2^s(x_{n})$, and
  $(R:C)(x_i,x_{i+1})$ for $i=1, \ldots, n$. 
\end{itemize}

@@

We evaluate the computational model described in steps 1--6 above over 4 different domains.
%
% *Fill up general details in 1--6 that don't change from problem to problem
%how $\S$ obtained
The sample set $\S$
% s obtained following one of two possible strategies.
% In the \emph{exhaustive} sampling strategy, $\S$
contains, for every one of the training instances $P$ in $\Q$,
the first $m$  states expanded by a standard breadth-first search from the initial state in $P$,
plus all the states along an optimal plan $\pi^*$ which is separately computed to ensure that $\S$ 
contains at least one goal state. 
All successor states of states in $\S$ are also added to $\S$.
%
For the goal marking scheme that yields the smaller theory $T_G(\S, \F)$, the states that are marked as
goal-relevant are those in $\pi^*$.

%
% In the \emph{random} sampling strategy, a large number $M$ of states are generated, potentially exhausting the full state space,
% and then a certain number $m \ll M$ of them is sampled uniformly at random. If no goal state is found among those $m$,
% one random goal state from the larger set is drawn at random and added into the sample.
% \textcolor{red}{\bf **** What if $M$ doesn't have a goal? ****}

@@

\alert{Details on the FOND planner, QNP translation, etc.}

@@

@@

\newcommand{\rowspacing[1]}{&&&&&&&&&&&&&&&&\\[\dimexpr-\normalbaselineskip+2pt]}

\begin{tabular}{rrrrrrrrrrrrrrrrr}
% @{\extracolsep{3pt}}

&$I$ & $\abs{\S}$ & $k$ & $\abs{\F^k}$ & \multicolumn{2}{c}{$T$} & \multicolumn{2}{c}{$T_G$} &  $T_{\text{SAT}}$ & $\abs{F}$ & $\abs{A_F}$ & $T_{\text{trans}}$  & \multicolumn{2}{c}{$Q^+_F$}  & $T_{\text{FOND}}$
& $\abs{\pi}$ \\ %

\rowspacing 
\cline{6-7} \cline{8-9} \cline{14-15}%
\rowspacing

 & &     &      &         & $\#V$ & $\#C$           & $\#V$ & $\#C$             &     &&&&  $\#Act$ & $\#At$&& \\%

\rowspacing \hline \rowspacing
\multirow{1}{*}{$\Q_{clear}$}
& 1     &     927 & 8  & 322 & 535K & 59.6M & 7.7K & 767K   &  0.01 & 3 & 2   &  - & - & - & - & - \\% Total complexity of F: 8

\rowspacing \hline \rowspacing
\multirow{1}{*}{$\Q_{on}$}
& 3 &        420  & 8 & 657 & 128K & 25.8M & 18.3K &     3.3M    &  0.02&  5 & 7   &  - & - & - & - & -\\% Total complexity of F: 18
% Max-sat problem has 128217 variables and 25825428 unique clauses (with repetitions: 25825428). Top weight is 4577

\rowspacing \hline \rowspacing
\multirow{1}{*}{$\Q_{gripper}$}    
& 2 &         403 & 8 & 130 & 93K & 4.7M & 8.1K &   358K    &  0.01 & 4 & 5&  - & - & - & - & -\\% Total complexity of F: 10

\rowspacing \hline \rowspacing
\multirow{1}{*}{$\Q_{reward}$}
& 2 &         568 & 8 & 280 & 184K & 11.9M & 15.9K & 1.2M   &  0.01 & 2 & 2 &  - & - & - & - & -\\% Total complexity of F: ?
\end{tabular}

}
\caption{{
  Experimental Results on 4 different generalized planning problems. 
  $I$: number of training instances; 
  $\abs{\S}$: sample set size, in total number of transitions;
  $k$: max. feature comlexity; $\abs{\F^k}$: size of the pool of features;
  $\#V$, $\#C$: Number of variables and clauses of the theories $T(\S,\F)$ and $T_G(\S,\F)$;
  $T_{\text{SAT}}$, $T_{\text{FOND}}$: computation time (sec.) of the SAT and FOND solvers, resp.;
  $\abs{F}$: number of selected features;
  $\abs{A_F}$: number of abstract actions;
  $T_{\text{trans}}$: time (sec.) to generate the FOND problem $Q^+_F$;
  $\#Act$, $\#At$: number if actions and atoms in $Q^+_F$;
  $\abs{\pi}$: size of the policy.
%  
  All figures that depend on the SAT theory are given for $T_G(\S,\F)$.
}}
\label{tab:exp-result-data}
\end{table*}
% 2018-09-05 00:54:08 INFO     Selected (states / goals / optimal tx): 220 / 34 / 20

@@

\paragraph{Clearing a block.}
The generalized problem $\Q_{clear}$ aims at achieving the goal $clear(x)$ for any block $x$
in the Blocksworld.
We take the standard STRIPS representation with primitive predicates $on(a, b)$, $clear(b)$, $ontable(b)$, $holding(b)$ and $handempty$.
%
With one single instance $\Q_{clear}$ with 5 blocks, we are able to learn
an abstract action space with features:

\begin{itemize}
\item $H: \abs{holding}$: whether any block is being held,
\item $X: \abs{holding \sqcap \set{x}}$: whether block $x$ is being held,
\item $n(x): \abs{\exists on^* . \set{x}}$: number of blocks above $x$.\footnote{
Action and features names are assigned manually to increase readability, based on the denotations of the involved concepts.
}
\end{itemize}

\noindent The resulting action model has two actions:

\begin{itemize}
\item \emph{pick-above-$x$}: \tuple{\neg X, \neg H, n(x) > 0; n(x) \downarrow},
\item \emph{place-aside}: \tuple{\neg X, H; \neg H},
\end{itemize}

\noindent 
The model is provably correct with respect to the generalized $\Q_{clear}$, but incomplete, as it lacks e.g.
an action to pick block $x$. However, it allows us to obtain the following policy from the FOND translation $Q^+_F$:

\alert{Display policy here},

\noindent which will alternatively \emph{pick-above-$x$} and \emph{place-aside} the picked block 
until block $x$ is clear. This can be proven to \emph{achieve the goal from any starting block configuration, for any number of blocks} in 
$\Q_{clear}$.

% Action 1: PLACE-ASIDE
%         PRE: NOT holding(a), bool[holding]
%         EFFS: NOT bool[holding]
% 
% Action 2: PICK-FROM-A
%         PRE: NOT bool[holding], NOT holding(a), n(a) > 0
%         EFFS: DEC n(a), bool[holding]

@@

\paragraph{Stacking two blocks from different towers.}
The problem $\Q_{on}$ aims at achieving a goal of the form $on(x,y)$
in the Blocksworld for any two blocks $x$ and $y$.
To simplify, we assume that $x$ and $y$ never start being in the same tower.
We take the same STRIPS representation as above. From 3 different training instances with up to 14
blocks, we are able to learn an abstract space based on the following 5 features:

\begin{itemize}
\item $X$, $n(x)$, $n(y)$: as in $\Q_{clear}$,
\item $E: handempty$: whether gripper is empty,
\item $XY: [(\exists on^{-1} . \set{x})\sqcap \set{b}]$: whether $x$ is on $y$.
\end{itemize}

\noindent Interestingly, the last feature is exactly a concept-based representation of the actual STRIPS goal $on(x,y)$.
The corresponding action model $A_F$ is:

\begin{itemize}
\item \emph{pick-above-$x$}:  \tuple{\neg X, \neg XY, E, n(x) > 0, n(y)>0; n(x) \downarrow, \neg E  }
\item \emph{pick-above-$y$}:  \tuple{\neg X, \neg XY, E, n(x) = 0, n(y)>0; n(y) \downarrow, \neg E  }
\item \emph{put-$x$-on-$y$}:  \tuple{X, \neg XY, \neg E, n(x)=0, n(y)=0 ; n(y) \uparrow, \neg X, E, XY}
\item \emph{pick-$x$}:  \tuple{;}
\item \emph{put-$x$-on-table}:  \tuple{;}
\item \emph{put-aside-1}:  \tuple{;}
\item \emph{put-aside-2}:  \tuple{;}

\end{itemize}

% Action 1 [PUT-ASIDE-1]:
%         PRE: NOT bool[handempty], NOT holding(a), NOT on(a, b)_2, n(a) = 0
%         EFFS: bool[handempty]
% 
% Action 2 [PUT-ASIDE-2]:
%         PRE: NOT bool[handempty], NOT holding(a), NOT on(a, b)_2, n(a) > 0, n(b) > 0
%         EFFS: bool[handempty]
% 
% Action 3 [PICK-A]:
%         PRE: NOT holding(a), NOT on(a, b)_2, bool[handempty], n(a) = 0, n(b) = 0
%         EFFS: NOT bool[handempty], holding(a)
% 
% Action 4 [PUT-A-ONTABLE]:
%         PRE: NOT bool[handempty], NOT on(a, b)_2, holding(a), n(a) = 0, n(b) > 0
%         EFFS: NOT holding(a), bool[handempty]
% 
% Action 5 [PICK-FROM-ABOVE-A]:
%         PRE: NOT holding(a), NOT on(a, b)_2, bool[handempty], n(a) > 0, n(b) > 0
%         EFFS: DEC n(a), NOT bool[handempty]
% 
% Action 6 [PICK-FROM-ABOVE-B]:
%         PRE: NOT holding(a), NOT on(a, b)_2, bool[handempty], n(a) = 0, n(b) > 0
%         EFFS: DEC n(b), NOT bool[handempty]
% 
% Action 7 [PUT-A-ON-B]:
%         PRE: NOT bool[handempty], NOT on(a, b)_2, holding(a), n(a) = 0, n(b) = 0
%         EFFS: INC n(b), NOT holding(a), bool[handempty], on(a, b)_2

\alert{ongoing}

@@

\alert{Display policy here}

@@

\begin{itemize}
\item $C: \exists carry . \top$ (number of balls carried by the robot), 
\item $X: at\_robby \sqcap \set{x}$ (whether robot in target room),
\item $G: \abs{free}$ (number of empty grippers), and
\item $B: \exists at . \neg \set{x}$ (number of balls not in target room),
\end{itemize}

@@

\begin{itemize}
\item \emph{drop-ball(s)-at-$x$}: \tuple{C>0, X;  C\downarrow, G \uparrow}
\item \emph{move-to-$x$-half-loaded}: \tuple{\neg X, B=0, C>0, G>0;   X}
\item \emph{move-to-$x$-fully-loaded}: \tuple{\neg X, C>0, G=0;   X}
\item \emph{pick-ball-not-in-$x$}: \tuple{\neg X, B > 0, G > 0;   B \downarrow, G \downarrow, C\uparrow}
\item \emph{drop-$x$}: \tuple{X, C=0, G > 0;   \neg X}
\end{itemize}
\noindent \alert{Action model to be checked}

@@

\alert{Display policy here}

@@

\alert{*** TO BE FINISHED ***}
